AusTraits: A curated plant trait database for the Australian flora

### 2021-04-28 scripts/update_author_list.Rmd
Update data to v3.0.0, address reviews

```{r}
authors_lead <- read_csv("data/lead_authors.csv")

@@

authors <- bind_rows(authors_lead %>% mutate(acknowledge=FALSE), 
                     data_contributors %>% filter(! (name %in% authors_lead$name))
  ) %>% 
  rename(affiliation_dataset = affiliation)
```

```{r}
affiliations_sheet <- 
  googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1nYE5V7utbExcfGmsfILjoXdVsEMDi5CLF_H-uE57EOo/edit#gid=280623389") %>% 
  filter(!is.na(name))

@@

# Check who hasn't responded
authors2 %>% filter(!acknowledge, !(name %in% responses_sheet$name)) %>% pull(name)

authors3 <- 
  authors2 %>% 
  mutate(
    # no response
    acknowledge = ifelse(!(name %in% responses_sheet$name), TRUE, acknowledge)
  )

>>>>

```{r}
load_data()

authors_lead <- read_csv("data/lead_authors.csv")

@@

authors <- bind_rows(authors_lead %>% mutate(acknowledge=FALSE), 
                     data_contributors %>% filter(! (name %in% authors_lead$name))
  ) %>% 
  rename(affiliation_dataset = affiliation)

affiliations_sheet <- 
  googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1nYE5V7utbExcfGmsfILjoXdVsEMDi5CLF_H-uE57EOo/edit#gid=280623389") %>% 
  filter(!is.na(name))

@@

# Check who hasn't responded
authors2 %>% filter(!acknowledge, !(name %in% (responses_sheet$name))) %>% pull(name)

authors3 <- 
  authors2 %>% 
  mutate(
    # no response
    acknowledge = ifelse(!(name %in% (responses_sheet$name)), TRUE, acknowledge)
  )
